---
title: "Agoro coding challenge"
output: html_notebook
---

**This R-notebook has results for the Agoro coding challenge. It includes all the related R scripts with documentation for each step.**

## Introduction

The objective of the challenge is _to develop and document an optimal sampling strategy to obtain the mean SOC content for all cropland in Iowa, with a 95% confidence interval being smaller or equal to 15% of the mean._

An optimized sampling strategy needs to take into account the heterogeneity of the area being measured, specifically in terms of SOC content. SOC itself or variables known to correlate with SOC can be used to characterize this heterogeneity.

The approach used here is similar to that in the provided publication (Gruijter et al. 2016). The study uses a map of C content with associated uncertainty to optimize:

* number of strata 
* stratum boundaries
* total sampling size
* within strata sampling size

While Gruijter et al. 2016 aim to maximize an expected profit taking into account sequestered C price, sampling costs and uncertainties in measurements, the objective here is simpler: we only need to find the minimum number of samples that will give a confidence interval (CI) of less than 15% of the mean.

The main objective-related variables are:

* Target universe: entire cropland area in Iowa
* Target variable: (top)soil organic carbon (SOC)
* Target parameter: sampling uncertainty


## Methods

#### Type of sampling

Following Gruijter et al. 2016, I chose a design-based sampling approach, thus excluding a model-based approach (so no previous assumption about spatial distribution). 

In addition, I also apply a stratification (Stratified Simple Random Sampling, StSRS), so that the entire area is divided into strata with simple random sampling applied in each. Stratification becomes useful when the data is known or suspected to be clustered, so that the variance within groups is smaller than the overall variance. This is expected for soil characteristics (think soil types).

As per discussed in Gruijter et al. 2016, bulking of soil samples is excluded. In particular, this method impedes a proper calculation of optimal sampling numbers across strata.

#### Confidence interval calculation

To calculate the confidence interval one needs some information about the variance of the target variable (organic C stocks) in the region of interest. If no direct data is available, some options (from worst to best) are:

1. making an assumption (a best guess) about the population distribution
2. using other variables as proxy data
3. using predictions of the target variable

The available data are:

* Köppen-Geiger climate classification for the period 1988-2017. World coverage.
* Crop mask: cultivated area for 2020 (https://nassgeodata.gmu.edu/CropScape/)
* Terrain: elevation (DEM) and wetness. Only pointer to online resource
* Soil: soilgrid data for clay and SOC. 250m scale

While clay can be used as a proxy for SOC, we already have SOC predictions (soilgrids.org at a 250m resolution), which are surely better than any prediction we can now make for this large region. So we use the predictions directly to estimate variance.

With this data, the sampling variance can be estimated as:

**Sampling variance**  
V(x_bar) = SUM{h=1 -> H} ((N_h / N)^2 * S_h^2 / n_h)

where x_bar is the mean of x, H is number of strata, N_h is size (number of grid points) of stratum h, N is total size (sum of all strata), S_h is standard deviation of x in stratum h, and n_h is sample size allocated to stratum h.  
However, this formula does not take into account the uncertainty in the model predictions, since S only describes the spatial variance. For this reason, data of organic carbon stock (OCS) uncertainty was downloaded from soilgrids.org, specifically the 0.05 quantile of the prediction probability distribution. Here I assumed the errors are normally distributed and so derived a mean error standard deviation per stratum (E_h), included in the formula above as:

**Sampling variance with error standard deviation**  
V(x_bar) = SUM{h=1 -> H} ((N_h / N)^2 * (S_h^2 + E_h^2) / n_h)

We then can get the confidence interval for a given confidence level (in this case 95%):

**Confidence Interval (CI)**  
x_bar +- t * (S / sqrt(n))  

where t is the t-score calculated form the confidence and n.

#### Stratification method

The following approaches can be taken to stratify the area of interest:

1. *Compact geographical stratification*  
This approach is only useful if there is no data available for the region. This is not our case.

2. *Stratification by ancillary variables*
This approach is useful of we have related ancillary data but not estimates of the target variable itself. In our case, we have SOC estimates from SoilGrids250m (soilgrids.org).

3. *Stratification by a map of predictions*
This approach improves over the previous option, as it already provides the 'best estimate' of SOC content distribution in the area. However, it does not take into account prediction uncertainties.

4. *Stratification by a map of predictions with uncertainties*
This approach is ideal as it takes uncertainties in predictions into account. However, according to Gruijter et al. 2016 the computation is slow for large grids, as in this case, and the code is not available. This option can be explored given more time (described in Gruijter et al. 2015).

I thus used the 3rd option (*Stratification by a map of predictions*) applying a k-means clustering (R package stats). 

To find the best number of strata (clusters) I applied an iterative approach, as suggested in Gruijter et al. 2016 but with a different selection criteria. Gruijter et al. 2016 determine the number of samples (n) that optimizes a "return on investment" by taking into account the cost of sampling. Here instead, the criteria is to find the design with the lowest n that still gives a 95% confidence at 15% of the mean. The approach from Gruijter et al. 2016 is somewhat more sophisticated (would require more time to implement) but also makes some assumptions that are critical (see discussion).

Specifically, for a given stratification level and n, an optimal allocation is found with:

**Optimal allocation size for stratum h**  
n'_h = n * (N_h * S_h) / (SUM{h=1 -> H} (N_h * S_h))

where N_h is the total grid point in stratum h, S_h is the standard deviation in stratum h, and H is the total strata.

For each stratification, n is iteratively increased from a defined minimum, until the condition CI/mean < 0.15 is met. The stratification with the lowest n is selected as optimal.

### Step by step procedure

Start by loaded all required packages
```{r message=FALSE, warning=FALSE}
library(rgdal)
library(terra)
library(raster)
library(tidyverse)
```

#### Processing of geospatial data

* The area of interest is the entire cropped surface of Iowa. A shape file of Iowa was thus obtained from: https://catalog.data.gov/dataset/tiger-line-shapefile-2016-state-iowa-current-county-subdivision-state-based  
* To obtain a smaller crop map file, data was downloaded for Iowa 2020 from https://nassgeodata.gmu.edu/CropScape 
* OCS mean and OCS 0.05 percentile data where downloaded from soilgrids using a Python script 

This step checks the land use map values to determine what is crop and what not. It then writes out a new file.  
(for code meaning, see https://www.nass.usda.gov/Research_and_Science/Cropland/metadata/metadata_ia20.htm).  
Two plots are created: one showing all land use data and the next showing cropland against background.

```{r}
# Set to false if output files already exist
subset_crop <- FALSE
download_ocs <- FALSE

crop_file <- 'data/crop_mask/CDL_2020_19/CDL_2020_19.tif'
crop <- rast(crop_file)
plot(crop)
if(subset_crop) {
  # Subset cropped areas ---
  
  cr_vals <- terra::values(crop)
  cr_uni <- terra::unique(cr_vals)
  rm(cr_vals)
  
  # Codes for land use obtained from https://www.nass.usda.gov/Research_and_Science/Cropland/metadata/metadata_ia20.htm
  notcrop <- c(0, 7, 8, 9, 15, 16, 17, 18, 19, 20, 40, 62, 63, 64, 65,
               73, 78, 79, 80, 81, 82, 83, 84, 85, 86, 87, 88, 89, 90,
               91, 92, 93, 94, 95, 96, 97, 98, 99, 100, 101, 102, 103,
               104, 105, 106, 107, 108, 109, 110, 111, 112, 113, 114,
               115, 116, 117, 118, 119, 120, 121, 122, 123, 124, 125, 
               126, 127, 128, 129, 130, 131, 132, 133, 134, 135, 136,
               137, 138, 139, 140, 141, 142, 143, 144, 145, 146, 147, 
               148, 149, 150, 151, 152, 153, 154, 155, 156, 157, 158,
               159, 160, 161, 162, 163, 164, 165, 166, 167, 168, 169, 
               170, 171, 172, 173, 174, 175, 176, 177, 178, 179, 180,
               181, 182, 183, 184, 185, 186, 187, 188, 189, 190, 191,
               192, 193, 194, 195, 196, 197, 198, 199, 200, 201, 202,
               203, 251, 252, 253, 255)
  iscrop <- c(1, 2, 3, 4, 5, 6, 10, 11, 12, 13, 14, 21, 22, 23, 24, 25,
              26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39,
              41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 
              55, 56, 57, 58, 59, 60, 61, 66, 67, 68, 69, 70, 71, 72, 
              74, 75, 76, 77, 204, 205, 206, 207, 208, 209, 210, 211, 
              212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 
              223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233,
              234, 235, 236, 237, 238, 239, 240, 241, 242, 243, 244, 
              245, 246, 247, 248, 249, 250, 254)
  
  cr_yes <- cr_uni[cr_uni %in% iscrop]
  cr_no <- cr_uni[cr_uni %in% notcrop]
  
  # Set all non-crop values to NA
  # crop[crop %in% cr_yes] <- 1
  crop[crop %in% cr_no] <- 0
  
  # plot(crop)
  terra::writeRaster(crop, 'data/workfiles/cropland-iowa.tif', overwrite=TRUE)
} else {
  cropfile <- 'data/workfiles/cropland-iowa.tif'
  crop <- rast(cropfile)
}
plot(crop)
```

Here the Python script to download OSC data is called and the data is loaded. An Iowa shape file is loaded and reprojected to the required coordinate system, then used to crop the OSC data. The crop map data is resampled to fit the resolution of the OCS grid (from 30m to 250m) and then used to select (mask) the OSC data. The final data (organic carbon stocks for cropland in Iowa) is plotted (tC / ha).
```{r message=FALSE, warning=FALSE}
# To download data, call python script
if (download_ocs) {
system("/home/fernando/anaconda3/bin/python3 soilgrids_WCS-2.0-ocs_mean.py")
system("/home/fernando/anaconda3/bin/python3 soilgrids_WCS-2.0-ocs_Q0.05.py")
}

# Read in the ocs mean and error data
ocs_file <- 'data/workfiles/soilgrids_ocs_mean_iowa_approx.tif'
ocs <- raster(ocs_file)
names(ocs) <- "ocs_m"
# GDALinfo(ocs_file)

ocserr_file <- 'data/workfiles/soilgrids_ocs_Q0.05_iowa_approx.tif'
ocserr <- raster(ocserr_file)
names(ocserr) <- "ocs_err"
# GDALinfo(ocserr_file)

# Load shapefile and set projection
# iowa_sh <- vect("data/shapefiles/tl_2016_19_cousub/tl_2016_19_cousub.shp")
iowa_sh <- shapefile("data/shapefiles/tl_2016_19_cousub/tl_2016_19_cousub.shp")
iowa_sh <- spTransform(iowa_sh, proj4string(ocs))  # Use same projections (coordinate system)

# Crop data
ocs <- rast(ocs)
ocserr <- rast(ocserr)
iowa_sh <- vect(iowa_sh)
ocs <- terra::crop(ocs, iowa_sh)
ocs <- terra::mask(ocs, iowa_sh)
ocserr <- terra::crop(ocserr, iowa_sh)
ocserr <- terra::mask(ocserr, iowa_sh)

# Change the resolution to match ocs data and subset the ocs data using the crop mask
crop2 <- terra::resample(crop, rast(ocs), method='near')
# ocserr <- terra::resample(ocserr, rast(ocs), method='near')
ocs <- terra::mask(x = ocs, mask = crop2, maskvalue=0)
ocserr <- terra::mask(x = ocserr, mask = crop2, maskvalue=0)

# check results
plot(ocs)
plot(ocserr)
```

The error standard deviation is derived from the 0.05 percentile and mean OCS data. The data is then written to file.
```{r}
# Lets convert 0.05 percentile to standard deviation assuming a normal distribution of the error:
ocserr_sd <- (ocserr-ocs)/(-1.645)  #  -1.645 value of Z at 0.05 percentile

# Fifth, we write out to file
terra::writeRaster(ocs, 'data/workfiles/soilgrids_ocs_mean_iowa.tif', overwrite=TRUE)
terra::writeRaster(ocserr_sd, 'data/workfiles/soilgrids_ocserr_sd_iowa.tif', overwrite=TRUE)
```


#### Optimization procedure

Several settings can be adjusted here. E.g. the input data files, confidence level required and minimum/maximum strata or samples.
```{r}
# Settings ======
test_id     <- "test1"  # used for naming output files
ocs_file    <- 'data/workfiles/soilgrids_ocs_mean_iowa.tif'
ocserr_file <- 'data/workfiles/soilgrids_ocserr_sd_iowa.tif'
use_prederr <- TRUE

conf_lev   <- 0.95  # confidence level required
max_cif    <- 0.15  # maximum allowed confidence interval as fraction of the mean
n_mps      <- 3     # minimum number of sampling points allowed per strata
min_H      <- 2     # minimum number of strata
max_H      <- 10    # number of strata to test
max_n      <- 1000  # maximum number of total samples
sample_inc <- 1     # sample number increment per iteration. In case processing time becomes critical.

```

Several functions are defined here, mostly related to the main equations used.
```{r}
# Function definitions ========
get_km_clust <- function(d, c) {
  # Function returns a clustering based on k_means
  # d: data to be clustered
  # c: number of centriods (clusters)
  set.seed(42)
  kmeans(x = na.exclude(d), centers = c, iter.max = 500, nstart = 5) #, algorithm = "Lloyd")
}

get_stratstats <- function(df) {
  df_out <- df %>%
    group_by(stratum) %>%
    summarize(stratum = mean(stratum), stratum_sd = sd(X), stratum_var = sd(X)^2,
              stratum_size = length(X), stratum_errsd = mean(X_sd)) %>%
    drop_na(stratum_sd)
}

get_sampvar <- function(H, N_H, N, S_H, n_H) {
  # Function returns the sampling variance for a stratified design
  # H: scalar for number of strata
  # N_H: vector of stratum sizes (number of grid points)
  # N: scalar for total grid points (sum of all strata) 
  # S_H: vector of standard deviation of ocs by stratum
  # n_H: vector of sample size allocated to each stratum
  sampvar <- 0
  for(i in 1:H) {
    v_h <- (N_H[i]/N)^2 * (S_H[i])^2 / n_H[i]
    sampvar <- sampvar+v_h
  }
  return(sampvar)
}

get_sampvar2 <- function(H, N_H, N, S_H, n_H) {
  # Same as get_sampvar but with a finite population correction term (only important for small grids)
  sampvar <- 0
  for(i in 1:H) {
    v_h <- (N_H[i]/N)^2 * ((N_H[i] - n_H[i]) / N_H[i]) * ((S_H[i])^2 / n_H[i])
    sampvar <- sampvar+v_h
  }
  return(sampvar)
}

get_sampvar3 <- function(H, N_H, N, S_H, E_H, n_H) {
  # Function returns the sampling variance for a stratified design
  # H: scalar for number of strata
  # N_H: vector of stratum sizes (number of grid points)
  # N: scalar for total grid points (sum of all strata) 
  # S_H: vector of standard deviation of ocs by stratum
  # E_H: vector of mean standard deviation in ocs prediction error by stratum
  # n_H: vector of sample size allocated to each stratum
  sampvar <- 0
  for(i in 1:H) {
    v_h <- (N_H[i]/N)^2 * ((S_H[i])^2 + E_H[i]^2) / n_H[i]
    sampvar <- sampvar+v_h
  }
  return(sampvar)
}

get_optsampalloc <- function(H, N_H, S_H, n_tot) {
  # Optimal sample distribution (sizes) for all strata h n’_h = n * (N_h * S_h) / (SUM(h=1 -> H) {N_h * S_h})
  # H: scalar for number of strata
  # N_H: vector size H of size (total number of grid points) of stratum h
  # S_H: vector size H of standard deviations for each stratum
  
  sum_sdn <- 0  # sum of standard deviations times number of samples
  for(i in 1:H) {
    x <- N_H[i] * S_H[i]
    sum_sdn <- sum_sdn + x
  }
  opt_n <- rep(NA, length = H)  # vector to hold outputs
  for(i in 1:H) {
    opt_n[i] <- n_tot * (N_H[i] * S_H[i]) / sum_sdn
  }
  return(as.integer(round(opt_n)))
}

get_confint <- function(conf_lev, sampvar, n_tot) {
  # Two-sided confidence interval calculation
  t <- qt(1-(1-conf_lev)/2, n_tot-1)  # the t-score from students distribution
  se <- sqrt(sampvar) / sqrt(n_tot) # standard error
  ci <- t * se * 2  # Multiplied by 2 to get the full interval length
}
```

The main optimization function.  
This function iterates over the defined stratification levels and uses a while loop for number of samples to find the optimal value.
A "best" combination is selected. Results returned include: 

* stratification of all grid points for optimal design
* samples numbers (density) for optimal design
* statistics for all tested stratifications

```{r}
optim_sampling <- function(df_in, conf_lev, max_ci, n_mps, min_H, sample_inc) {
  # This function obtains the minimum amount of total samples necessary to attain the value of max_ci
  # It also returns the sampling density for each stratum 
  # Returns a list containing: 
  #   1. dataframe with grid values and optimized strata values
  #   2. dataframe with strata numbers and optimized samples per strata
  
  # Working variables
  H_all   <- tibble(nstrata=min_H:max_H, n_opt = NA, svar = NA, cif = NA, ci = NA)  # table holding output values
  nH      <- NA  # Number of strata
  n_tot   <- NA  # Number of total samples
  ocs_avg <- mean(df_in$X, na.rm = TRUE)  # overall mean organic carbon stock
  N_tot   <- sum(!is.na(df_in$X))  # N total number of grid points
  H_levs  <- min_H:max_H  # stratification levels to test
  
  for(i in 1:length(H_levs)) {
    
    nH <- H_levs[i]
    cat("Optimizing at stratification:", nH, "\n")
    
    # if(nH == 20) browser()  # debug line
    
    # Create strata
    clust <- get_km_clust(d = df_in$X_raw, c = nH)
    df_in$stratum[which(!is.na(df_in$X_raw))] <- as.integer(clust$cluster)
    
    # Get statistics for current stratification
    H_stats <- get_stratstats(df_in)
    
    iter1 <- 1
    # target_reached <- FALSE  # not used
    
    while(TRUE) {
      
      # Calculate the total sampling size
      if(iter1==1) {n_tot <- n_mps * nH} else {n_tot <- n_tot + sample_inc}
      
      # print(n_tot)  # for debug
      
      # Stop if maximum allowed samples reached
      if(n_tot > max_n) {
        cat(paste0("Reached maximum number of allowed samples at stratification: ", nH, "\n"))
        break
      }
      
      # if(n_tot == 64 & nH == 6) browser()  # debug line
      
      # Get the optimal allocation
      opt_n <- get_optsampalloc(H = nH, N_H = H_stats$stratum_size, S_H = H_stats$stratum_sd, n_tot = n_tot)
      opt_n[opt_n < n_mps] <- n_mps  # if we don't get the minimum n per stratum, add where necessary
      H_stats$opt_n <- opt_n
      n_tot2 <- sum(H_stats$opt_n)  # recalculate to fix any difference after rounding
      
      # Get the overall sampling variance as a function of stratified sampling
      if(use_prederr) {
        samp_var <- get_sampvar3(H = nH, N_H = H_stats$stratum_size, N = N_tot, S_H = H_stats$stratum_sd,
                                 E_H = H_stats$stratum_errsd, n_H = H_stats$opt_n)
      } else {
        samp_var <- get_sampvar(H = nH, N_H = H_stats$stratum_size, N = N_tot, S_H = H_stats$stratum_sd,
                                n_H = H_stats$opt_n)  
      }
      
      # Get confidence interval
      ci <- get_confint(conf_lev = conf_lev, sampvar = samp_var, n_tot = n_tot2)
      cif <- ci / ocs_avg
      
      # Check if cif is same or lower than the maximum allowed confidence interval
      if(cif <= max_cif) {
        # target_reached <- TRUE
        H_all$n_opt[i] <- n_tot2
        H_all$svar[i] <- samp_var
        H_all$cif[i] <- cif * 100
        H_all$ci[i] <- ci
        break
      }
      
      iter1 <- iter1+1
      
    }
    
    # if(target_reached) {} 
    
  }
  
  # First select strata with lowest n_opt
  H_sel <- H_all[H_all$n_opt == min(H_all$n_opt, na.rm=TRUE),] 
  # If more than one selected, take the case with more strata (err on the safe side)
  H_best  <- H_sel[H_sel$nstrata == max(H_sel$nstrata, na.rm=TRUE),]
  
  # Recalculate clusters and sampling for the selected case ----- (deduplicate code?)
  
  # Create strata
  clust <- get_km_clust(d = df_in$X, c = H_best$nstrata[1])
  df_in$stratum[which(!is.na(df_in$X))] <- as.integer(clust$cluster)
  
  # Get statistics for best stratification
  Hb_stats <- get_stratstats(df_in)
  
  # Get the optimal allocation
  
  opt_n <- get_optsampalloc(H = H_best$nstrata[1], N_H = Hb_stats$stratum_size, S_H = Hb_stats$stratum_sd, n_tot = H_best$n_opt[1])
  opt_n[opt_n < n_mps] <- n_mps  # if we don't get the minimum n per stratum, add where necessary
  Hb_stats$opt_n <- opt_n
  
  cat(" Confidence interval equal or less than the target (" ,  max_cif * 100, "% ) was found.\n")
  cat(" CI = ", H_best$ci, "\n",
      "CIrel = ", H_best$cif * 100, "%\n",
      "Mean SOC stocks = ", ocs_avg, "\n",
      "Total strata = ", H_best$nstrata, "\n",
      "Total samples = ", H_best$n_opt, "\n",
      "Samples per strata = ", Hb_stats$opt_n, "\n"
  )
  
  return(list(Strata_out = df_in, Strata_stats = Hb_stats, Strata_all = H_all))
  
}
```

Here the necessary raster data is loaded and extracted to a data frame. A histogram shows that the OCS data is skewed so a log transform is applied.
```{r}
# Load and execute ============

# Read in the data of SOC predictions over the target area
r_ocs_m <- rast(ocs_file)
r_ocs_err <- rast(ocserr_file)

# Get the values as a matrix
ocs_raw <- data.frame(
  X_raw = as.vector(terra::values(r_ocs_m)),
  X_sd_raw = as.vector(terra::values(r_ocs_err)),
  stratum = NA )  # add a variable to hold stratum values

# Check the data
hist(ocs_raw$X_raw, 80, main = "org C means")
hist(ocs_raw$X_sd_raw, 80, main = "org C standard deviations")

# Log transform to get normal distributions
ocs_tran <- ocs_raw
small <- 1 # add to avoid 0 values for log transform
ocs_tran <- ocs_tran %>%
  mutate(X = log(X_raw+small), X_sd =  log(X_sd_raw+small))

hist(ocs_tran$X, 80, main = "log org C means")
hist(ocs_tran$X_sd, 80, main = "log org C standard deviations")

```

Finally, the sampling optimization is run and the results saved. The first table shows the strata of the optimal design, including size and number of samples. The second table shows results for all tested stratifications.
```{r}
# Call the sampling optimization function
optim_out <- optim_sampling(df_in = ocs_tran, conf_lev = conf_lev, max_ci = max_ci,
                           n_mps = n_mps, min_H = min_H, sample_inc = sample_inc)

print(optim_out[[2]])
print(optim_out[[3]])

# Create raster of strata
ocs_H <- terra::setValues(r_ocs_m, optim_out[[1]][[2]])

# Save results ======
info_file <- paste0("data/workfiles/", test_id, "_strata_optim_info.csv")
write_csv(optim_out[[2]], info_file)
strata_file <- paste0("data/workfiles/", test_id, "_ocs_strata.tif")
terra::writeRaster(x = ocs_H, strata_file, overwrite = TRUE)
```


##Discussion

Re-sampling at the same points is not recommended by (Gruijter et al. 2016). With different points there is no temporal auto-correlation, so the term rho becomes zero:  
V(x_bar_delta) = V(x_bar_t1) + V(x_bar_t2) 

**Variance of estimated difference**
V(x_bar_delta) = V(x_bar_t2 - x_bar_t1)  
               = V(x_bar_t1) + V(x_bar_t2) - 2 * rho * sqrt( V(x_bar_t1) * V(x_bar_t2) )  


## References 

J.J. de Gruijter, A.B. McBratney, B. Minasny, I. Wheeler, B.P. Malone, U. Stockmann, Farm-scale soil carbon auditing, Geoderma, Volume 265, 2016, Pages 120-130

J. J. De Gruijter, B. Minasny, A. B. Mcbratney, Optimizing Stratification and Allocation for Design-Based Estimation of Spatial Means Using Predictions with Error, Journal of Survey Statistics and Methodology, Volume 3, Issue 1, March 2015, Pages 19–42

